A finite-state morphological transducer for Kyrgyz

### 2012-03-14 paper/paper.tex
I guess this form is God

%FIXME: * Some remaining transducer issues
% maybe fixed now?
Also, despite the good coverage, there are still a number of grammatical forms that have not been implemented into the transducer.  For example, one such form is historically the negative of the eyewitness past tense, but is now used (mostly with a question clitic) in a certain type of modal expression;\footnote{A surprised contradictory expression, like ``Did I not just clean the floor??''} this cannot be tagged as the negative of the eyewitness past tense, since a suppletive form is tagged that way.  Other shortcomings of the transducer are that it is not set up to deal with affixes on abbreviations or numerals in cypher (e.g., АКШнын \eng{The USA's}, 100гө \eng{to 100}) or capitalisation changes on lemmas that occur in different word classes (e.g., Финландия \eng{Finland}, but финландиялык \eng{Finnish}).

>>>>

%FIXME: * Some remaining transducer issues
% maybe fixed now?
Also, despite the good coverage, there are still a number of grammatical forms that have not been implemented into the transducer.  For example, one such form is historically the negative of the eyewitness past tense, but is now used (mostly with a question clitic) in a certain type of modal expression;\footnote{A surprised contradictory expression, like ``Did I not just clean the floor??''} this cannot be tagged as the negative of the eyewitness past tense, since a suppletive form is tagged that way.  Other shortcomings of the transducer are that it is not set up to deal with affixes on abbreviations or numerals/digits (e.g., АКШнын \eng{The USA's}, 100гө \eng{to 100}) or capitalisation changes on lemmas that occur in different word classes (e.g., Финландия \eng{Finland}, but финландиялык \eng{Finnish}).
